\subsection{Motivation} \label{subsec:motivation}

This work intends to minimize the price of robust ground robot localization in
unstructured environments by using sensors that are relatively inexpensive,
imply a low overhead, and might be needed for other functionalities of the
robot: acoustic odometry. Many ground mobile robots will be equipped with sound
sensors for the purpose of human-robot interaction \cite{VoiceForklift}, at the
same time, audio signals have been extensively studied, resulting in very
efficient methods for their processing.

Increasing the robustness of robot localization in unstructured environments
without significantly increasing its price would make this technology more
accessible. Which complies with the 9th and 10th Sustainable Development Goals:
Promotes innovation without increasing the inequalities between small and big
producers \cite{SDG}.

At the same time, this work focuses on wheeled robots on loose sandy terrain.
Although strides have been made into exotic forms of legged robots, wheels or
tracks still form the basis for robot locomotion \cite{Sanchez09}. Wheeled
mobile systems are useful for practical applications compared to legged systems
because of the simplicity of the mechanisms and control systems and efficiency
in energy consumption \cite{Masayoshi2006}. However, wheeled systems'
performance depends on the traction between the wheels and the ground. If there
is not enough traction, the wheel will slip and the efficiency will decrease.
Traction is a special concern when the robot is expected to move over granular
non-cohesive loose soil, also known as sandy terrain. Which is the case for
planetary missions \cite{Amar2007}, construction site applications, and
agricultural robots, among others.