\subsection{Discussion} \label{subsec:discussion}

The proposed Acoustic Odometry system proves to be a viable auxiliary source of
odometry for wheeled robots in loose sandy terrain. \Cref{fig:other-methods}
and \cref{fig:VO-challenge} show that audio-based odometry is more accurate
than wheel odometry, and its accuracy can be comparable to state-of-the-art
commercially available visual-based methods and that it can be more accurate
than visual odometry in the presence of dynamic objects and lightning. 

This work only evaluates the performance of a shallow convolutional neural
network with different layer sizes. But other architectures be more suitable
for the task. Specially transformers \cite{vaswani2017attention} which have
been used in speech recognition \cite{kim2022squeezeformer} and visual odometry
tasks \cite{li2020transformer}. Moreover, neural networks may not even be
needed, a simpler algorithm may be used with sufficient accuracy and lower
computational cost.

The selected model behavior changes from one device to another. Devices that
output an audio signal with a higher power tend to result in higher speed
predictions, as can be seen in \cref{fig:high-slip}, while the overall
predicted curve is very similar. Meaning that even if the absolute value of the
predicted velocity is not accurate, the model is able to recognize slippage
conditions across different devices. Even with devices not present during
training, as is the case in \cref{fig:other-methods}, where none of the devices
shown in the evaluation were present during training. This indicates that
fine-tuning \cite{TL2016} a model with the device where it will be deployed
might significantly increase its performance. Similarly, using wheel odometry
to estimate the wheel angular speed while using the proposed system to identify
the wheel slippage may improve the performance as well.

White noise affects the performance of the proposed system, as could
be expected. Nevertheless, a considerably large noise power compared to the
signal power does not make the selected model unusable. As it can be seen in
\cref{fig:noise-effect}, where a noise with a power 10 times the one of the
audio signal (SNR -10 dB) only significantly affects the predictions on
speeds close to 0. This indicates that white noise only significantly affects
the prediction of speeds under a threshold determined by the signal-to-noise
power ratio.

Finally, this work can be compared with other odometry methods. On one hand,
only \cite{marchegiani2018a} proposes an audio-based odometry method, claiming
an average absolute error of 0.065 m/s when predicting velocities, which is
comparable to the average ATE 0.001m accumulated over the 66 15ms long audio
frames contained in one second. But this work also shows that the actual
average RPE in a 1 second window is 0.005m. However, it remains unknown the
performance of the proposed system on rotational movement and under the
presence of multiple moving wheels. This comparison should also be taken with a
grain of salt as no common benchmarking data exists.

On the other hand, the method presented in \cite{Ojeda2006}, where wheel
slippage is identified using the motor current and compensated in the wheel
odometry computation, still outperforms the proposed system while being a
computationally inexpensive method. They demonstrate accumulated drift of up to
1\% of the traveled distance using the same range of longitudinal velocities
under 0.07 m/s, while the proposed system results in an average error of
16\% of the traveled distance across all devices and evaluation recordings.
On the other hand, the authors mention that current-based slippage detection
fails to correctly identify a wheel slipping over rocks instead of sand.
Audio-based methods do have the potential to identify wheel slippage in both
scenarios and \cref{para:recommendations} discusses several improvements that
could be applied to the proposed system in order to improve its performance.